\documentclass[runningheads]{llncs}
\bibliographystyle{splncs04}

\usepackage{glossaries}

% DEFINE ACRONYMS HERE. Params: label, short version, long version
\newacronym{CNN}{CNN}{Convolutional Neural Network}
\newacronym{CC}{CC}{Color Constancy}


\usepackage{Paper}


\graphicspath{ {./images/} }

\begin{document}

\title{An Investigation of Color Constancy for Image Classification}
\titlerunning{Color Constancy Classification}

\author{
    Uzairu Abubakar\inst{1} \and
    Niklas Bieck\inst{1} \and
    Fabiano Junior Maia Manschein\inst{1} \and
    Yuya Takagi\inst{1} \and
    Damien Muselet\inst{1}\orcidID{0000-0001-7803-1171}
}
\authorrunning{U. Abubakar et al.}

\institute{
    Université Jean Monnet Saint-Étienne, 10, rue Tréfilerie – CS 82301, 42023 Saint-Etienne Cedex 2, France
    \email{https://www.univ-st-etienne.fr/fr/index.html}
}



\maketitle

\begin{abstract}
    Color constancy, the process of determining the true color of light in an image
    and adjusting it to match a reference illuminant, is a widely researched area.
    A key argument in favor of this technique is its potential to enhance the training
    of other image processing techniques by eliminating the need to learn variations
    caused by different lighting conditions. To validate this claim, we conduct a
    comprehensive analysis by comparing the performance and training times of image
    classification models using a dataset of flower images. They are particularly
    suitable for this study due to the crucial role of color in their identification.
    The comparison is conducted with and without the application of color constancy
    methods as a preprocessing step. We also compare the results with the use of batch
    normalization as an alternative to color constancy.
    Our results show no particular gain made by our methods, but we believe further research
    is warranted.
\end{abstract}

% Here's my suggested structure for the paper. Subject to change, specially titles.
\input{sections/introduction.tex}  % Introduction
\input{sections/similar_studies.tex}  % Previous related studies on applying CC as preprocessing
\input{sections/experiment.tex}  % The experiment: pipeline, datasets, CC and CLF models
\input{sections/results.tex}  % Results of the experiment
\input{sections/conclusion.tex}  % Conclusion and outlook

%force figures before references
\clearpage

\bibliography{references}
\end{document}